Manuscript

### 2014-08-08 inst/simulation/manuscript.Rmd
...

```{r figure-5}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
credibilityIntervals <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)

@@

>>>>

```{r credible-intervals}

@@

```{r figure-5}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- cbind(a, b)
p <- ggplot(credibilityIntervals, aes(scenario, Proportion, colour=CredibleInterval)) + geom_point() +
  theme_minimal() + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-5.png", width=4, height=4)
```
